\documentclass[10pt]{article}

\usepackage{hyperref}
\hypersetup{
    colorlinks,breaklinks,
    linkcolor=black,urlcolor=blue,
    anchorcolor=MidnightBlue,citecolor=blue,
    pdftitle={Richard Paul Bronosky},
    pdfauthor={Richard Paul Bronosky},
    pdfsubject={Resume},
    pdfkeywords={resume, linux, mobile, iOS, Android, python, Docker, AWS}
}

\usepackage[top=0.5in, bottom=0.25in, left=0.5in, right=0.5in]{geometry}
\usepackage{xfrac}
\usepackage{setspace}
\usepackage{ifthen}

\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\hyphenchar\font=-1
\setstretch{1}
\usepackage{booktabs}
\usepackage{topcapt}

\newfont{\skillfont}{cmr10 at 9pt}
\newfont{\linkfont}{cmr10 at 6pt}

\newcommand{\heading}[4]{
    \begin{center}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
    &\huge{\textbf{\sc{#1}}}&\\
    \href{mailto:#2}{\small #2} & \small #3 & \small Mobile: #4\\
    \hline\hline
    \end{tabular*}
    \end{center}
}

\newcounter{blocktitlechildren}
\newcommand{\blocktitle}[1]{
    \blocktitlechild{2mm}
    \setcounter{blocktitlechildren}{0}
    {{\sc{#1}\vspace{1.5mm}\hrule}\vspace*{1.5mm}}
}

\newcommand{\blocktitlechild}[2][]{
    \ifthenelse{\equal{\value{blocktitlechildren}}{0}}{}{\vspace{#2}#1}
    \addtocounter{blocktitlechildren}{1}
}

\newcommand{\skillnew}[2]{
    \blocktitlechild{1mm}
    \begin{tabular}
        {p{2cm}p{16cm}}
        \noindent\raggedright{\skillfont{#1}} & #2
    \end{tabular}
}

\newcommand{\sectionheader}[4]{
    \blocktitlechild{2mm}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2\\
    \emph{#3} & \emph{#4}
    \end{tabular*}
}

\newcommand{\sectionsub}[2]{
    \blocktitlechild{1.4mm}
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \emph{#1} & \emph{#2}
    \end{tabular*}
}

\newenvironment{longtext}[1]{\small {#1}}

\setlength{\parindent}{0in}


\begin{document}
\heading{Richard Paul Bronosky}
{Richard@Bronosky.com}
{53 Blackberry Lane, Douglasville, GA 30134}
{404-922-7866}

\blocktitle{Objective}
\begin{longtext}
    I have a vision for what is next for my company.
    I want to see all of our content responsive to screens of any size.
    Our concept of mobile should encompass Connected TVs, Blu-ray players, set-top boxes, and game consoles.
    I'm going to convince you to incorporate into apps features that only apps can have, that justify them being apps.
    I want to see Medley provide tools for curating content for devices that makes it a natural part of the workflow.
    We're going to build an architecture with inconsequential publishing delays. They will no longer be discussed.
    I have seen this company through "the draining of the swamp" and the toilsome have-to-dos. I want to be the person who leads us into the want-to-dos.
%    The Mobile Architect position gives clarity to the role I have served technically since 2010.
%    It plays into my strength of deep diving into extremely complex systems and making them accessible to various audiences.
%    It answers questions I have had about my role in vendor and site relationships.
\end{longtext}
\vspace{2mm}
\begin{longtext}
    I have been employed as a web professional since 1996. I have not been this excited about the state of technology in 16 years. I will lead Cox into this space with Speed, Passion, and Courage.
\end{longtext}
\vspace{2mm}

\blocktitle{Overview}
\begin{longtext}
    Manage systems engineers and software developers ---
    Optimize SDLC and workflow ---
    Develop web and mobile applications ---
    Web and mobile architecture ---
    Develop and deploy iPhone and Android apps ---
    Develop and deploy PhoneGap HTML5+CSS3+JS apps ---
    Manage vendors and contractors ---
    Administer various Unix and Gnu/Linux ---
    Administer virtualization hosts and guests ---
    Optimize RAID, swap, and cache ---
    MySQL schema design, tuning, replication, disaster planning, and HA ---
    Audit application code for security and performance ---
    Transform and migrate data ---
    Manage SLAs as both the client and vendor ---
    Strong verbal and written communication skills ---
    Excellent troubleshooting and debugging skills ---
    Unrepentant command line addict
\end{longtext}
\vspace{2mm}

\blocktitle{Skills}

\skillnew{Languages}{
    Python,
    JavaScript,
    CSS,
    HTML,
%    XML,
    shell scripting,
    RegEx,
    Objective-C,
    Java,
    PostgreSQL,
    Oracle SQL \& PL/SQL,
%    ColdFusion,
    Ruby,
    PHP,
    PERL \& CGI,
    C/C++,
    \LaTeX
}

\skillnew{Systems \& Software}{
    Gnu/Linux (RedHat, Debian),
    Solaris,
    FreeBSD,
    OpenBSD,
    MacOS X,
    iOS,
    Android
%    Windows 95/98/NT

%    MySQL High Availability and FS wizardry,
%    Continuent UniCluster,
    HTTP,
    TCP/IP,
    Apache,
    SSH tunnel wizardry,
    cURL,
    tcpdump,
    BASH,
    Django,
    jQuery,
    VIM,
    Gnu Screen,
    tmux,
    Adobe Photoshop and Illustrator,
    Xcode,
    GIT/SVN/CVS,
    Ruby on Rails,
    Tomcat,
    MySQL,
    VMWare,
    Xen,
    LVM,
    BIND DNS,
    Splunk,
    Nagios,
    Cacti,
    Macromedia Flash
}

\blocktitle{Experience}

\sectionheader
{Cox Media Group Digital \& Strategy Team / Atlanta Journal-Constitution}
{Atlanta, GA}
{Software Development Manager}
{November 2009 to Present}
\begin{longtext}
manage $\sfrac{1}{4}$ of a \~{}30 developer team;
Encourage and inspire developers and vendors to give great service.
Improve performance through coaching.
Maintain SDLC process.
Present and Teach.
Architect and develop software.
Lead mobile architecture and technical strategy.
Recommend and review application architecture and code.
Study complex systems and make them accessible to various audiences.
Manage vendors.
%code, protocol, and process archaeology;
Script functional tests.

\end{longtext}
\sectionsub
{Internet Systems Manager \& MySQL DBA}
{July 2008 to November 2009}
\begin{longtext}
Administer Gnu/Linux servers.
Manage a department of system administrators.
Virtualize existing web infrastructure.
Plan infrastructure and capacity.
Audit and deploy developer code and data migrations.
Troubleshoot network issues.
\end{longtext}
\sectionsub
{MySQL DBA}
{January 2007 to July 2008}
\begin{longtext}
Administer MySQL.
Optimize developer code.
Maintain high availability and performance.
Develop extra Django and Rails projects.
\end{longtext}

\sectionheader
{Yahoo!}{Atlanta, GA telecommute to Sunnyvale, CA}
{Technical Yahoo!}
{March 2004 to January 2007}
\begin{longtext}
Manage teams, development, projects, SLAs.
Develop web applications.
Administer FreeBSD, Gnu/Linux, Apache, MySQL.
\end{longtext}

\sectionheader
{Apple Computer}{Atlanta, GA}
{Business Sales Specialist}
{March 2004 to June 2004}
\begin{longtext}
Exploit my expertise to lure businesses away from Microsoft products for the greater good of the universe.
\end{longtext}

\sectionheader
{Lanier Worldwide}{Atlanta, GA}
{Web Application Developer}
{October 2002 to March 2004}
\begin{longtext}
Manage and train developers on CVS, security policies, and best practices.
Develop custom CMS.
\end{longtext}

\sectionheader
{MedCenterDirect}{Atlanta, GA}
{Lead Solutions Developer}
{December 2000 to October 2002}
\begin{longtext}
Develop applications, portals, and commerce solutions.
Architect custom deployment strategy.
Script manual data migrations.
\end{longtext}

\blocktitle{Education}

\sectionheader
{University of Kentucky}{}
{Computer Engineering and Systems Analysis}
{1997}
\hspace*{\fill}
\vspace{1mm}
\href{http://references.bronosky.com}{http://references.bronosky.com}
\end{document}
