% Congratulations! You are among the elite few who will ever see the source code
% that generated the resume PDF that most others stop at. Your curiosity in me
% makes me more interested in you. When we speak, be sure to mention that you
% saw this message. That said, let me make a disclaimer. The state of this code
% is very unpredictable. I customize my resume for every recipient I send it to.
% Most of the customizations get `git stash`-ed, `git branch`-ed, or `git
% rebase`-ed away. But, there is always a fair bit of tech-debt in this code. I
% like to believe that someday I will make this a gleaming example of what a
% resume template should be. But, I find the Docker container that I built for
% generating the PDF to be much more interesting to polish. Have you seen it?
% It's in this repo. Unlike this code, it's a great example of the work I do.

\documentclass[letterpaper,10pt]{article}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{parskip}
\setlength{\parindent}{0mm}
\setlength{\parskip}{0mm}
\usepackage{hyperref}
\hypersetup{
    colorlinks,breaklinks,
    linkcolor=black,urlcolor=blue,
    anchorcolor=MidnightBlue,citecolor=blue,
    pdftitle={Bruno Bronosky},
    pdfauthor={Bruno Bronosky},
    pdfsubject={Resume},
    pdfkeywords={resume, Linux, mobile, iOS, Android, python, Docker, Kubernetes, AWS, Azure, DevOps}
}

\usepackage[top=8mm, bottom=10mm, left=12mm, right=10mm]{geometry}
%\usepackage{showframe} %debug
\usepackage{nicefrac}
\usepackage{setspace}
\usepackage{ifthen}

\usepackage{fancyhdr}
\setlength{\footskip}{10pt}
\fancyhf{}

\setlength{\fboxsep}{-\fboxrule}
\newcommand{\debux}[1]{\fbox{#1}}

\newcommand{\lineDouble}[0]{\hrule\vspace{2pt}\hrule\vspace{1.5pt}}
\newcommand{\autohref}[1]{\href{#1}{#1}}

\lfoot{
    \lineDouble
    \begin{tabularx}{\textwidth}{l>{\raggedleft\arraybackslash}X}
        \autohref{https://github.com/RichardBronosky/resume} &
        \autohref{https://stackoverflow.com/cv/brunobronosky} \\
    \end{tabularx}
}
\pagestyle{fancy}

\setlength{\tabcolsep}{0mm}
\hyphenchar\font=-1
\hyphenation{DevOps}
\setstretch{1}
\usepackage{booktabs}
\usepackage{topcapt}
\usepackage{tabularx}
\usepackage{colortbl}
\newcolumntype{L}[0]{>{\raggedright\arraybackslash}X}
\newcolumntype{C}[0]{>{\centering\arraybackslash}X}
\newcolumntype{R}[0]{>{\raggedleft\arraybackslash}X}

\newcommand{\sizeA}[0]{\fontsize{6pt}{7pt}\selectfont}
\newcommand{\sizeB}[0]{\fontsize{7pt}{8pt}\selectfont}
\newcommand{\sizeC}[0]{\fontsize{8pt}{9pt}\selectfont}
\newcommand{\sizeD}[0]{\fontsize{9pt}{10pt}\selectfont}
\newcommand{\sizeE}[0]{\fontsize{10pt}{12pt}\selectfont}
\newcommand{\sizeF}[0]{\fontsize{11pt}{13pt}\selectfont}

\AtBeginDocument{\sizeD}
\newcommand{\heading}[4]{
    \begin{tabularx}{\textwidth}{LCR}
        &\huge{\textbf{\sc{#1}}}&\\
        \href{mailto:#2}{#2} & #3 & Mobile: #4\\
    \end{tabularx}
    \lineDouble
    \vspace{5pt}%
}

\newcounter{skipfirstcounter}
\newcommand{\skipfirst}[1]{
    \ifthenelse{\equal{\value{skipfirstcounter}}{0}}{#1}{#1}
    \addtocounter{skipfirstcounter}{1}
}

\newcommand{\blocktitle}[1]{
    \setcounter{skipfirstcounter}{0}
    \begin{tabularx}{\textwidth}{lR}
        {\sizeF\sc{#1}} & \noindent\hrulefill\\
    \end{tabularx}
}

\newcommand{\blockOverview}[1]{%
    \blocktitle{Overview}%
    \vspace{0.4mm}%
    \begin{tabular*}{\textwidth}{p{\textwidth}}%
        #1%
    \end{tabular*}%
    \vspace{2mm}%
}%

\newcommand{\blockSkills}[1]{
    \blocktitle{Skills}
    \begin{tabular*}{\textwidth}{p{22mm}p{171.6mm}}%
        #1% no slashes here because I addlinespace later
    \end{tabular*}%
    \vspace{2.4mm}%
}

\newcommand{\skillgroup}[2]{{\sizeE{#1}} & #2\\\addlinespace[1.6mm]}

\newcommand{\skillgrouplast}[2]{{\sizeE{#1}} & #2\\}

\newcommand{\blockExperience}[1]{
    \blocktitle{Career}%
    #1%
    \vspace{2mm}%
}

\newcommand{\blockEducation}[1]{
    \blocktitle{Education}%
    #1%
}

\newcommand{\sectionheaderfirst}[2]{
    \begin{tabularx}{\textwidth}{Lr}%
    % TODO: Make this shorter on the first one
    %\skipfirst{\addlinespace[1.1mm]}
    \textbf{#1} & #2\\%
    \end{tabularx}%
}

\newcommand{\sectionheader}[2]{
    \vspace{2mm}%
    \sectionheaderfirst{#1}{#2}%
}

\newcommand{\sectionsub}[2]{
    {\def\arraystretch{1}
        \begin{tabularx}{\textwidth}{Lr}
        \rowcolor[rgb]{.9,.9,.9}
        \emph{#1} &
        \rule{0mm}{3.2mm} % This is a kludge that must be adjusted if the font size changes
        \emph{#2} \\
        \addlinespace[0.4mm]
        \end{tabularx}
    }
}

\newcommand{\sectionbody}[1]{
    #1
    \vspace{1mm}
}

\newcommand{\rating}[1]{\nicefrac{#1}{5}\kern 0.05em}


\begin{document}
\heading{Bruno Bronosky}
{Bruno@Bronosky.com}
{2525 MacLaren Cir, Dunwoody, GA 30360}
{404-992-7866}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Overview %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\blockOverview{
    Cloud computing with Amazon Web Services, Heroku, Docker, and Kubernetes ---
    Data center orchastration with Chef and Ansible ---
    Plan infrastructure and capacity ---
    OpenVPN, SSH tunneling, network security ---
    %Troubleshoot network issues ---
    DBA for Cassandra, MongoDB, PostgreSQL, and MySQL ---
    Administer various Unix and Gnu/Linux ---
    Administer virtualization hosts and guests ---
    Optimize RAID, swap, and cache ---
    Code, protocol, and process archaeology ---
    Manage systems engineers and software developers ---
    Manage vendors and contractors ---
    Manage SLAs as both the client and vendor ---
    Study complex systems and make them accessible to various audiences ---
    Review and recommend application architecture and code ---
    Maintain SDLC process ---
    Develop web and mobile applications ---
    Architect cloud, web, and mobile solutions ---
    Develop and deploy iPhone and Android apps ---
    Develop and deploy Cordova and React Native HTML5+CSS3+JS apps ---
    Audit and deploy developer code and data migrations ---
    Transform and migrate data ---
    Audit application code for security and performance ---
    Strong verbal and written communication skills ---
    Excellent troubleshooting and debugging skills ---
    Unrepentant command line addict ---
    Ambiguity Assassin
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Skills %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\blockSkills{
    \skillgroup{Development}{
        \rating{5}bash/PowerShell/shell scripting,
        \rating{3}Node.js,
        \rating{4}Python,
        \rating{2}Java/Android,
        \rating{4}PostgreSQL,
        \rating{4}Oracle SQL \& PL/SQL,
        \rating{3}Django,
        \rating{4}JavaScript,
        \rating{4}CSS,
        \rating{4}HTML,
        \rating{4}jQuery,
        \rating{3}Ruby,
        \rating{2}Ruby on Rails,
        \rating{4}PHP,
        %\rating{2}PERL \& CGI,
        \rating{2}C/C++/Objective-C,
        \rating{3}\LaTeX
    }

    \skillgroup{Operations}{
        \rating{4}Gnu/Linux (RedHat, Debian),
        %\rating{1}Solaris,
        \rating{3}FreeBSD,
        %\rating{2}OpenBSD,
        \rating{5}MacOS X,
        \rating{4}Windows 10 WSL2,
        \rating{4}Amazon Web Services (EC2, CF+Lambda@Edge, API Gateway, Lambda, DynamoDB, ELB, ECS, S3, Route53, Sagemaker),
        \rating{2}Azure (Blob storage, CDN, Container Instances, Functions),
        \rating{4}Kubernetes,
        \rating{3}Cassandra,
        \rating{3}MongoDB,
        \rating{3}ELK,
        %\rating{2}Tomcat,
        \rating{4}MySQL,
        \rating{4}Apache,
        \rating{3}VMWare,
        \rating{3}xen,
        \rating{3}LVM,
        \rating{4}BIND DNS,
        %\rating{3}New Relic,
        %\rating{3}Splunk,
        %\rating{3}Cacti,
        \rating{3}Sensu,
        \rating{4}Nagios
    }

    \skillgrouplast{Concepts}{
        \rating{4}DevOps,
        \rating{4}CI/CD,
        \rating{5}vim,
        \rating{5}git,
        \rating{4}Terraform,
        \rating{4}Chef,
        \rating{3}Ansible,
        %\rating{2}Puppet,
        \rating{4}Packer,
        \rating{4}Docker,
        \rating{4}Serverless,
        \rating{5}HTTP,
        \rating{4}TCP/IP,
        \rating{5}SSH tunnel wizardry,
        \rating{4}RegEx,
        \rating{5}cURL,
        \rating{3}tcpdump,
        %Gnu Screen,
        \rating{4}tmux,
        \rating{2}AI/ML,
        \rating{3}IoT,
        \rating{5}Adobe Photoshop \& Illustrator,
        \rating{2}Autodesk Fusion360,
        \rating{1}Mach3 CNC,
        \rating{1}Blender,
        \rating{1}Eagle CAD,
        \rating{2}Xcode
    }
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Career %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\blockExperience{
    \sectionheaderfirst
    {Rooms To Go}{Dunwoody, GA}
    \sectionsub
    {Principal DevOps Engineer}
    {November 2018 to Present}
    \sectionbody{
    Direct and train a department of DevOps Engineers and SREs.
    Train developers to follow DevOps & CI/CD processes.
    Architect Hybrid-Cloud and Multi-Cloud infrastructure.
    Set and enforce security practices.
    Develop tools and services in bash, Node.js, Python, and Go.
    Design, build, and deploy Docker containers, API Gateways.
    Automate and orchestrate infrastructure with Packer and Terraform.
    Build and maintain [Fargate] ECS, EKS, and Kubernetes clusters serving microservices.
    Manage AWS costs.
    Make and document changes to AWS infrastructure via aws-cli.
    Manage network security with AWS Security Groups, iptables, and OpenVPN.
    Maintain MongoDB and DynamoDB databases.
    }

    \sectionheader
    {MidAmerican Energy Services}{Dunwoody, GA}
    \sectionsub
    {DevOps Team Leader}
    {October 2016 to July 2018}
    \sectionbody{
    Orchestrate infrastructure with Packer, Terraform, Chef, and Ansible.
    Build and maintain Kubernetes clusters serving microservices.
    Develop tools in Python, Go, bash, awk, sed, CircuitPython, and Arduino.
    Build and maintain Cassandra, MongoDB, and MySQL databases.
    Build custom Raspberry Pi images for IoT devices sent to client locations.
    Design and CNC mill custom IoT hardware cases.
    }

    \sectionheader
    {Cox Media Group Technology / Atlanta Journal-Constitution}{Atlanta, GA}
    \sectionsub
    {Solution Architect, Mobile}
    {December 2012 to October 2016}
    \sectionbody{
    Develop mobile client and backend POCs.
    Architect and deploy cloud infrastructure.
    Develop and maintain original Open Source software projects.
    Workflow and process automation.
    Lead mobile architecture and technical strategy.
    Present and teach.
    }

    \sectionsub
    {Software Development Manager}
    {November 2009 to December 2012}
    \sectionbody{
    Manage $\nicefrac{1}{4}$ of a \~{}30 developer team.
    %Improve performance through coaching.
    %Encourage and inspire developers and vendors to give great service.
    Workflow automation scripting.
    Architect and develop software.
    }

    \sectionsub
    {Internet Systems Manager \& MySQL DBA}
    {July 2008 to November 2009}
    \sectionbody{
    Administer Gnu/Linux servers.
    Manage a department of sysadmins.
    Workflow automation and config management.
    }

    \sectionsub
    {MySQL DBA}
    {January 2007 to July 2008}
    \sectionbody{
    Administer MySQL.
    Optimize developer code.
    Maintain high availability and performance.
    Develop extra Django and Rails projects.
    }

    \sectionheader
    {Yahoo!}{Atlanta, GA telecommute to Sunnyvale, CA}
    \sectionsub
    {Technical Yahoo!}
    {March 2004 to January 2007}
    \sectionbody{
    Manage teams, projects, SLAs.
    Automate workflows.
    Develop web applications.
    Administer FreeBSD, Apache, MySQL.
    }

    \sectionheader
    {Apple Computer}{Atlanta, GA}
    \sectionsub
    {Business Sales Specialist}
    {March 2004 to June 2004}
    \sectionbody{
    Exploit my expertise to lure businesses away from Microsoft products for the greater good of the universe.
    }

    \sectionheader
    {Lanier Worldwide}{Atlanta, GA}
    \sectionsub
    {Web Application Developer}
    {October 2002 to March 2004}
    \sectionbody{
    Manage and train developers on CVS, security policies, and best practices.
    Develop CMS and software deployment system.
    }

    %\sectionheader
    %{MedCenterDirect}{Atlanta, GA}
    %\sectionsub
    %{Lead Solutions Developer}
    %{December 2000 to October 2002}
    %\sectionbody{
    %Develop applications, portals, and commerce solutions.
    %Architect custom deployment strategy.
    %Script data migrations.
    %}

    \sectionheader
    {Additional Professional Experience}{}
    \sectionsub
    {Various Software/Systems Engineering, Tech Support, and Graphics/Animation positions}
    %{August 1995 to December 2000}
    {August 1995 to December 2002}
    \sectionbody{
    Out of respect for your time, I've kept this resume to one page. See StackOverflow URL below or discuss during interview.
    }
}

%\blockEducation{
%    \sectionheaderfirst%
%    {University of Kentucky}{}%
%    \sectionsub%
%    {Computer Engineering and Systems Analysis}%
%    {1997}%
%}%
\end{document}
